\demes: a pain-free specification for complex demography

### 2021-06-14 paper.tex
Reworked software as a description list.

\section*{Extensions and future directions}

\subsection*{Software support for \demes}
\aprcomment{at time of publication. TBD...}
\begin{itemize}
    \item \msprime: coalescent simulation \citep{kelleher2016efficient}
    \item \stdpopsim: a collection of maintained species and demographic models,
        which includes a large number of models specified using \demes
        \citep{adrion2020community}
    \item \fwdpy: forward-time Wright-Fisher simulation \citep{thornton2014c++}
    \item \moments: compute expected diversity statistics (SFS, LD) and perform
        demographic inference using summary statistics
        \citep{jouganous2017inferring,ragsdale2019models}
    \item \dadi: compute the expected SFS and perform demographic inference using
        summary statistics \citep{gutenkunst2009inferring}
\end{itemize}

@@

\begin{itemize}
    \item \texttt{demesdraw} (\url{https://github.com/grahamgower/demesdraw.git})
    \item General framework for inference (have been working on that over in \moments,
        and perhaps it could be generalized to work with any simulation engine
    \item Defining distributions of parameter values, perhaps?
\end{itemize}

>>>>

% \begin{table}
% \begin{center}
% \begin{tabular}{llr}
% \msprime & \citep{kelleher2016efficient} & Coalescent simulator \\
% \stdpopsim & \citep{adrion2020community} & Library of standardised simulations \\
% \fwdpy & \citep{thornton2014c++} & Forward-time simulator \\
% \moments & \citep{jouganous2017inferring,ragsdale2019models}
%     & Demographic inference \\
% \dadi & \citep{gutenkunst2009inferring}  & Demographic inference \\
% \gadma & \citep{noskova2020gadma}  & Demographic inference \\
% \end{tabular}
% \end{center}
% \caption{Software supporting Demes as an input or output format.
% \jkcomment{This is a very rough first pass. It's not clear that a table is the
% right format for presenting this information, maybe a description
% list would be better instead?}}
% \end{table}

\subsection*{Software support for Demes}

\begin{description}
    \item[demes-python] A Python library for loading, saving, and working with
        Demes models. Includes conversion utilities for existing formats
        demographic model descriptions such as
        \texttt{ms}~\citep{hudson2002generating}.
    \item[demes-c] A C library for parsing Demes YAML descriptions.
    \item[demesdraw] A Python library for visualising Demes models
     (\url{https://github.com/grahamgower/demesdraw.git}).
\end{description}

\subsection*{Software implementing Demes}
At the time of writing, the following software implements the Demes
specification, as a supported input or output format.

\begin{description}
    \item[msprime:] Coalescent simulation
        \citep{kelleher2016efficient,kelleher2020coalescent}
    \item[stdpopsim:] A collection of community empirical data for species
        and demographic models specified in Demes format~\citep{adrion2020community}.
    \item[fwdpy11:] forward-time Wright-Fisher simulation \citep{thornton2014c++}
    \item[moments:] compute expected diversity statistics (SFS, LD) and perform
        demographic inference using summary statistics
        \citep{jouganous2017inferring,ragsdale2019models}.
    \item[$\partial$a$\partial$i] compute the expected SFS and
        perform demographic inference using
        summary statistics \citep{gutenkunst2009inferring}.
    \item[GADMA] Demographic inference \citep{noskova2020gadma}.
\end{description}

@@

\begin{itemize}
    \item General framework for inference (have been working on that over in \moments,
        and perhaps it could be generalized to work with any simulation engine
    \item Defining distributions of parameter values, perhaps?
\end{itemize}
